Juliacon Proceedings in Quarto

### 2023-11-14 template.qmd
basically done

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
abstract: |
  This document is a Quarto template demonstrating the `juliacon-proceedings` format.
year: 2022
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
---

>>>>

---
title: Juliacon Proceedings in Quarto
format:
  juliacon-proceedings-pdf:
    keep-tex: true  
  juliacon-proceedings-html: default
author:
  - name: Patrick Altmeyer
    affiliations:
      - Delft University of Technology
    orcid: 0000-0003-4726-8613
    email: p.altmeyer@tudelft.nl
    url: https://www.paltmeyer.com/
  - name: Cynthia C. S. Liem
    affiliations:
      - Delft University of Technology
abstract: |
  This document is a Quarto template demonstrating the `juliacon-proceedings` format.
year: 2022
keywords: [Template, Demo, Quarto, JuliaCon]
bibliography: bibliography.bib  
---

### 2023-11-14 template.tex
basically done

\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Juliacon Proceedings in Quarto},
  pdfauthor={Patrick Altmeyer},
  pdfkeywords={Template, Demo, Quarto, JuliaCon},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Juliacon Proceedings in Quarto}
\author{
Patrick Altmeyer~\orcidlink{0000-0003-4726-8613}\\Delft University of
Technology\\\href{mailto:p.altmeyer@tudelft.nl}{p.altmeyer@tudelft.nl}}
\date{}
\begin{document}
\maketitle

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon 2022 Proceedings},
    pdfauthor = {Patrick Altmeyer},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}

>>>>

\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Juliacon Proceedings in Quarto},
  pdfauthor={Patrick Altmeyer; Cynthia C. S. Liem},
  pdfkeywords={Template, Demo, Quarto, JuliaCon},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Juliacon Proceedings in Quarto}

\author[1]{Patrick Altmeyer}
\author[1]{Cynthia C. S. Liem}
\affil[1]{Delft University of Technology}
\date{}
\begin{document}
\maketitle

@@

% Hypersetup
\hypersetup{
    pdftitle = {Juliacon Proceedings in Quarto},
    pdfsubject = {JuliaCon 2022 Proceedings},
    pdfauthor = {Patrick Altmeyer, Cynthia C. S. Liem},
    pdfkeywords = {Template, Demo, Quarto, JuliaCon},
}
